\section{Quality Requirements}
\paragraph{This section looks st the manner in which the code is made and maintained}
\section{Maintainability}
	\begin{itemize}
		\item How flexible and extensible is the code and, can the system be easily maintained in future?
		\item The code is slightly cluttered with commenting providing some descriptions of the code making future changed slightly challenging.
	\end{itemize}
\section{Scalability}
	\begin{itemize}
		\item The system should be easily scalable to large systems from the University of Pretoria to even larger systems.
		\item The system is implemented quite simplistically and not rigid allowing for mass deployment
	\end{itemize}
\section{Performance Requirements}
	\begin{itemize}
		\item Reporting operations should take no more than 5 seconds while non-reporting operations should take less than (or equal to) 0.2 seconds.
		\item This system does not work so we cannot test.
	\end{itemize}
\section{Reliability and Availability}
	\begin{itemize}
		\item Should support fail-safe over safety of components and deployment without a single point of failure.
		\item There are no fail safes provided and the code is not completed (many TODO's).
	\end{itemize}
\section{Security}
	\begin{itemize}
		\item Check authentication against LDAP and flexible configurable authorization framework.
		\item No authorization is handled.
	\end{itemize}
\section{Auditability}
	\begin{itemize}
		\item The systems logs all requests and responses as stringified JSON object.
		\item Printing to the console is provided and their are some logging but not as JSON strings.
	\end{itemize}
\section{Testability}
	\begin{itemize}
		\item Must be testable through unit testing and integration tests. Should verify that pre and post conditions met.
		\item There is a general test file that checks for all pre and post conditions of the system.
	\end{itemize}
\section{Usability}
	\begin{itemize}
		\item The system should be intuitive and fun to use.
		\item This section is directed more towards the final end-product.
	\end{itemize}
\section{Integrability}
	\begin{itemize}
		\item The system should be able to easily integrate future requirements.
		\item The rigidity of the system would make it a problem for future integration.
	\end{itemize}
\section{Deployability}
	\begin{itemize}
		\item The system must be deployable on Linux servers, different database persistence environments and, diferent repositories for authentication credentials.
		\item The system is deployable on Linux server. Implementation for access to other environments does not seem to be provided.
	\end{itemize}
