
\paragraph{Requirement 1}
	\subparagraph{Expected Functionality}
	This test must provide the ability to assess a number of measures around individual Buzz Space contributions.
	
	\subparagraph{Actual Test output}
	This test was successful as it provides ways to create new ways in which a profile status is calculated for a BuzzSpace. The only problem was that the needed 			authorisation was not implemented where it must have been. Only lecturers are supposed to be able to create these new ways. 
		

\paragraph{Requirement 2}
	\subparagraph{Expected Functionality}
	Be able to use the newly created ways of calculating a status for a profile on a Buzz Space,
	
	\subparagraph{Actual Test output}
	This function was implemented successfully,  but the specific Buzz Space for which this new calculation method must  added was never specified.

\paragraph{Required Use Cases}
	\subparagraph{AssessProfile}
	Not a success because of the following contract services being denied:
	\begin{itemize}
			\item No authorisation was done, thus all users could add a new way of calculating a status and not lecturers only.
	\end{itemize}

	\subparagraph{setStatusCalculator}
	Not a success because of the following contract services being denied:
	\begin{itemize}
			\item The specific Buzz Space for which the status calculation method must be changed was never specified or used to change the method. 
	\end{itemize}	

	\subparagraph{getStatusForProfile}
	This use case was a success.
	
	\subparagraph{createAppraisalType}
	This use case was a success.
	
	\subparagraph{activateAppraisalType}
	This use case was not implemented in the file from the final commit.

	\subparagraph{assignAppraisalToPost}
	This use case was not implemented in the file from the final commit.

	\subparagraph{Test Coverage Analysis}
	33 percent of the use cases were implemented successfully

	

