\section{Quality Requirements}
\paragraph{This section looks st the manner in which the code is made and maintained}
\section{Maintainability}
	\begin{itemize}
		\item How flexible and extensible is the code and, can the system be easily maintained in future?
		\item The developers implemented their system very simplistically and provided comments with explanations of their code. The comments provided contain expected parameters, expected results and, potential throws.
	\end{itemize}
\section{Scalability}
	\begin{itemize}
		\item The system should be easily scalable to large systems from the University of Pretoria to even larger systems.
		\item Due to it's simplistic nature and implementation, the system could easily be scaled.
	\end{itemize}
\section{Performance Requirements}
	\begin{itemize}
		\item Reporting operations should take no more than 5 seconds while non-reporting operations should take less than (or equal to) 0.2 seconds.
		\item This system does not work so we cannot test.
	\end{itemize}
\section{Reliability and Availability}
	\begin{itemize}
		\item Should support fail-safe over safety of components and deployment without a single point of failure.
		\item The system itself completely failed as there were multiple errors.
	\end{itemize}
\section{Security}
	\begin{itemize}
		\item Check authentication against LDAP and flexible configurable authorization framework.
		\item No authorization is handled.
	\end{itemize}
\section{Auditability}
	\begin{itemize}
		\item The systems logs all requests and responses as stringified JSON object.
		\item They printed out whenever a function was called but not kept in a database.
	\end{itemize}
\section{Testability}
	\begin{itemize}
		\item Must be testable through unit testing and integration tests. Should verify that pre and post conditions met.
		\item Unit tests have been implemented but they do not succeed as the system itself is flawed.
	\end{itemize}
\section{Usability}
	\begin{itemize}
		\item The system should be intuitive and fun to use.
		\item This section is directed more towards the final end-product.
	\end{itemize}
\section{Integrability}
	\begin{itemize}
		\item The system should be able to easily integrate future requirements.
		\item The simplistic nature allows for this.
	\end{itemize}
\section{Deployability}
	\begin{itemize}
		\item The system must be deployable on Linux servers, different database persistence environments and, diferent repositories for authentication credentials.
		\item The system is deployable on Linux server.
	\end{itemize}
